### 2014-07-03 Choosing R3 Relations.tex
Lemma 4.6 for Weight 2 Cases

\begin{lem} (Analogue of 4.6) 
Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$. To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$. But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in W$_{\Gamma^{Op}}.$ Therefore, we are done.
\end{proof}

>>>>

\begin{lem} (Analogue of 4.6) 
Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$. To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$. But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{Op}}.$

For a triangle labeled as in Figure 8, by r'(1, 2) we have $$s_{1}s_{2}^{-1}s_{3}s_{2}s_{1}^{-1} = s_{2}^{-1}s_{3}s_{2}.$$ Hence $$s_{1}s_{3}s_{2}s_{3}^{-1}s_{1}^{-1} = s_{3}s_{2}s_{3}^{-1}.$$ But as before, this can occur if and only if $s_{1}^{-1}, s_{2}^{-1}, s_{3}^{-1}$ satisfy the relation r'(1, 3) in W$_{\Gamma^{Op}}$.

Finally, given a square labeled in figure 9 and the relations r'(1, 2) and r'(3, 4), we have 
\begin{align*}
& s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
&= s_{1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
&= s_{1}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{1}^{-1} \\
&= s_{1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2})s_{2}^{-1}s_{1}^{-1} \\
&= s_{1}s_{2}(s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1})s_{2}^{-1}s_{1}^{-1} \\
&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{2}s_{2}^{-1}s_{1}^{-1}s_{2} \\
&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}
\end{align*}
But this relation holds if and only if $s_{1}^{-1}, \dots, s_{4}^{-1}$ satisfy r'(2, 1) in W$_{\Gamma^{Op}}$. Therefore, we are done.
\end{proof}
